---
title: "GLM regression -Census data"
author: "Zoe"
date: "5/11/2021"
output: 
  prettydoc::html_pretty:
    theme: architect
    highlight: github

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE, warning = FALSE)

```

## R Markdown

```{r libraries}
library(plm)
library(data.table)
library(DT)
```


```{r import data}
# import data 
df = read.csv("weeks.csv")
num.lines <- 100
question.counter <- 0
```

```{r show dt}
dat <- fread("weeks.csv")
datatable(dat,rownames = TRUE)
```
```

```{r distribution of dv}
library(ggplot2)
ggplot(df, aes(x = Value)) +
    geom_density(alpha = .2, fill = "#FF6666")

```
The distribution of outcome looks pretty normal


```{r subset groups gender}
df_gender = subset(df, Group == 'gender')
df_gender

```

GLM by gender
```{r glm1 gender}
fit <- glm(Value ~ Subgroup+Week, data=df_gender, family=Gamma(link = 'log'))
summary(fit)
```

 GLM by Race
```{r subset groups race}
df_race = subset(df, Group == 'race')
df_race
```


```{r glm race}
fitrace <- glm(Value ~ Subgroup+Week, data=df_race, family=Gamma(link = 'log'))
summary(fitrace)

```

GLM by education

```{r subset groups education}
df_education = subset(df, Group == 'education')
```


```{r glm3 educaton}
fiteducation <- glm(Value ~ Subgroup+Week, data=df_education, family=Gamma(link = "log"))

summary(fiteducation)
```

GLM by age

```{r subset age groups}
df_age = subset(df, Group == 'age')
```


```{r glm age}
fitage <- glm(Value ~ Subgroup+Week, data=df_age, family=Gamma (link = 'log'))
summary(fitage)
```
